\documentclass[paper=a4]{scrartcl}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{morefloats}
\usepackage[section] {placeins}
\usepackage{caption}
\usepackage{todonotes} %todo notes

%%%%%%%%%%%%%%%%%%%%%%%%% Configuration %%%%%%%%%%%%%%%%%%%%%%
\lstset{
    basicstyle=\footnotesize,
    tabsize=2
}
\DeclareCaptionType{json}[Example][List of JSON Examples]
%\newenvironment{json}{}{}
%%%%%%%%%%%%%%%%%%%%%%%%%% Header %%%%%%%%%%%%%%%%%%%%%%%%%% 

%opening
\title{JEngine REST API Specification v2.0}
\author{BP2014W1 - Team}

\begin{document}

\maketitle

%\listoftodos %displaying open todos
\setcounter{totalnumber}{5}
%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%% 

%
%%
\begin{abstract}
	One goal of the JEngine was to provide a flexible API.
	Developers can use this API to build an UI or to control/use the engine from within another application.
	There are methods to configure, control and monitor processes and their instances.
	This document will provide a specification/documentation of the Rest-Interface, by providing the information about the allowed methods and examples .
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%% Overall API Structure %%%%%%%%%%%%%%%%%%%%%%%%%% 

%
%%
\section{Structure}
    \begin{centering}
		\label{tbl:structure}
		\centering
		\begin{tabular}{r|r}
			\texttt{http://domain:port/jengine/api/}&\texttt{interface/\{version\}}\\
			&\texttt{config/\{version}\}\\
			&\texttt{jcomparser/\{version\}}\\
			&\texttt{history/\{version\}}\\
			&\texttt{analytics/\{version\}}
		\end{tabular}
		\captionof{table}{API Core Path}
	\end{centering}
	The API is divided into four parts (Table \ref{tbl:structure}):
	\begin{enumerate}
		\item \textbf{Interface.}
			  The interface provides methods for creating and controlling instances of scenarios.
			  More information can be found in Chapter \ref{subsec:Interface}.
		\item \textbf{Config.}
			  This API can be used to configure a process model.
			  Currently the configuration is restricted to email tasks.
			  More information and examples can be found in Chapter \ref{subsec:Config}.
		\item \textbf{Comparser.}
			  The JEngine can be used to execute Production Case Management (PCM) models created with the \href{BP2014W1 processeditor.html}{JEDItor}\footnote{\url{BP2014W1 processeditor.html}}.
			  The JComparser is an interface between the core of the engine and the model repository provided by the JEDItor.
			  The JComparser provides and interface to view and load models from the repository.
			  More information and examples can be found in chapter \ref{subsec:Comparser}.
		\item \textbf{History.}
			  Detailed information about state changes of data object and activities of running and terminated scenario instances can be accessed via the history interface.
			  Chapter \ref{subsec:History} provides examples and detailed information.
	    \item \textbf{Analytics.}
			  to be explained. (framework for implementing analytic algorithms for analysing the PCM execution logs)
	\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%% Functions %%%%%%%%%%%%%%%%%%%%%%%%%% 

%
%%
\input{functions.tex}
	 
%%%%%%%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%%% 		
\end{document}
